\documentclass{article}
\usepackage{minted}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\DeleteFile}[2][]{}

\title{Java Operators}
\date{2021-02-24}
\author{Liv}

\begin{document}
    \maketitle
    \pagenumbering{arabic}

    \section{Questions and Exercises}

    \subsection{Consider the following code snippet.}
    \subsubsection{What are the values of i and n after the code is executed}
    The field 'i' is 11 and 'n' is 0.

    \subsubsection{What are the final values of i and n if instead of using the postfix increment operator (i++), you use the prefix version (++i))?}
    The field 'i' is 11 and 'n' is 1.

    \subsection{To invert the value of a boolean, which operator would you use?}
    \begin{minted}{java}
    Boolean inverted = !foo;
    \end{minted}

    \subsection{Which operator is used to compare two values, = or == ?}
    The '==' operator is.

    \subsection{Explain the following code sample.}
    \begin{minted}{java}
        result = someCondition ? value1 : value2;

        // Can be rewritten as
        if (someCondition) {
            result = value1;
        } else {
            result = value2;
        }
    \end{minted}

    \subsection{Operators may be used in building \_\_\_\_\_, which compute values.}
    In building expressions.

    \subsection{Expressions are the core components of \_\_\_\_\_.}
    They are the core components of statements.

    \subsection{Statements may be grouped into \_\_\_\_\_.}
    They may be grouped into blocks.

    \subsection{Statements are roughly equivalent to sentences in natural languages, but instead of ending with a period, a statement ends with a \_\_\_\_\_.}
    It ends with a semicolon.

    \subsection{A block is a group of zero or more statements between balanced \_\_\_\_\_ and can be used anywhere a single statement is allowed.}
    Statements between balanced braces.

    \subsection{In the following program, explain why the value "6" is printed twice in a row.}
    The value of '++i' increases immediately, while the value of 'i++' only increases in the next statement.

    \newpage
    \subsection{Write a program that accepts a price on the command line and prints out the appropriate tax and total purchase price.}

    \begin{minted}{java}
    public class SalesTax {
        public static void main(String[] args) {
            Scanner sc = new Scanner(System.in);
            System.out.println("Enter price");
            
            Double tax = 1.0825;
            Double price = sc.nextDouble();
            Double priceAfterTax = price * tax;
            System.out.println("Tax is: " + (priceAfterTax - price));
            System.out.println("Total cost is: " + priceAfterTax);
        }
    }
    \end{minted}

    \subsection{Write a program that takes a number of inches from the command line and converts it to centimeters.}

    \begin{minted}{java}
    public class InchesToCm {
        public static void main(String[] args) {
            Scanner sc = new Scanner(System.in);
            System.out.println("Enter inches");
            
            Double cmInInch = 2.54;
            Double inches = sc.nextDouble();
            System.out.println(inches + " inches is " + (inches * cmInInch) + "cm");
        }
    }
    \end{minted}
\end{document}